\Large \bf Apropos Replacement : Development of a full text search tool for man pages

### 2012-02-29 apropos_replacement.tex
Fix abstract
Language improvement

\subsection*{Abstract}
Manual pages are a key component of Unix like operating systems, they have
played a significant role in the success of Unix over the years. Man pages are
the most authentic source of reference for of a system administrator or a
programmer. However, so far, there has been a lack of good search tool to make
man pages more accessible. \\

@@

This paper discusses a new implementation of \textit{apropos} done by
Abhinav Upadhyay as part of
Google Summer of Code 2011. The goal of this project was to replace the
conventional apropos in NetBSD with a modern version which supports full text
searches. \\

@@

This simplified design of \textit{apropos} resulted in limited utility and
usability, as the searches are limited to the keywords defined in the NAME
section of the man pages. Only if the users know the exact keywords do they get
the appropriate results; otherwise most of
the times the searches are full of irrelevant results or possibly a dead end. 
In the modern
computing world where hard problems like searching the World Wide Web have been
solved [3] to a sufficient degree, it makes perfect sense to leverage the
advancement in technology in order to solve the problem. This problem is made
even simpler considering that the man pages consist of structured data. \\

@@

\subsection{Lack of support for free form queries}
As noted earlier the conventional \textit{apropos} is limited to the keywords
used in the NAME section of the man pages. This means that the users do not have
a whole lot of choice for specifying keywords in their queries. Besides they
cannot search for keywords which are not usually specified in the title of a man
page, for example a query like ``EINVAL'' would return no results. \\

{\tt \small
\lstset{language = sh, caption={No results for free form queries}}
\begin{lstlisting}
$ apropos ``add new user''
add new user: nothing appropriate

@@

\subsection{Lack of basic language support}
Another major limitation of the classical version of \textit{apropos} is that
it is not smart enough to provide basic natural language processing constructs,
like stemming or spelling corrections.
For example in the following listing it can be seen
that while \textit{apropos} returns the correct result for the query
\textit{``make directories''}, it fails when the keyword \textit{``directory''}
is used in place of \textit{``directories''}, even though the two words are based
on same root word. \\

{\tt \small
\lstset{language = sh, caption={No support for stems or words with same root},}
\begin{lstlisting}
$ apropos ``make directories''
mkdir (1) - make directories
$ apropos ``make directory''
make directory: nothing appropriate

@@

{\tt \small
\lstset{language = sh, caption={No spelling correction},}
\begin{lstlisting}
$ apropos ``copy strings''
stpcpy, stpncpy, strcpy, strncpy (3) - copy
strings
$ apropos ``coppy strings''
coppy strings: nothing appropriate
\end{lstlisting}
}

@@

\section{Solution: A new apropos}
This project proposes a very simple and straightforward solution to solve these
problems and make man pages more usable. The idea is to exploit the inherent
semantics and structure of the man pages. The \textit{mdoc(7)}
macros are semantically quite rich, those macros combined with the context of the surrounding section or context in which they have been used, can be used
as an indicator of the relevancy of the content. For example, the
{\tt \small
.Nm
}
macro when used inside of the
{\tt \small
NAME
}
section holds more significance than if used inside of any other section. Similarly the description of various \textit{errno} values in the
\textit{intro(2)} man page has more important information than the mention of
those \textit{errno} values in the
{\tt \small
RETURN VALUES
}
section of various man pages from section 3. In essence, it should be possible
to parse and extract the structurally meaningful data
out of man pages and index them in the form of an inverted index [4]. An
inverted index is a specialized data structure for building search engines. The index combined with a ranking algorithm which exploits the structured nature of the data to give back more relevant results to the user, can be used to build a
high quality search interface for manual pages.
Such a search tool will solve many of the problems associated with the conventional \textit{apropos(1)} as noted
before and discussed as follows: \\

@@

\section{Implementation Details}
Due to space constraints it is not possible to go into enough implementation
details, the most important components of this project are described in brief
in this section.

@@

\begin{description}
\item[Database Schema] \hfill \\
During the initial stage of the project, the structure of the database was kept
simple. The FTS table consisted of 3 columns:
{\tt
name, name\_desc, desc
}
The
{\tt
name
}
and
{\tt
name\_desc
}
columns stored the name of the man page and the one line description from the
{\tt
NAME
}
section, while the
{\tt
desc
}
column stored the content from the rest of the sections. This approach worked
quite well for a small set of man pages (for example the 4000 or so man pages in
the base set of NetBSD). However, as the number of documents were increased (for example including man pages from pkgsrc), the quality of search started deteriorating. This was mainly because bulk of the parsed data was being stored
in the same column in the database and the ranking algorithm had no way of
identifying more relevant results apart from the number of matches in any page. \\

To rectify this, first there was an attempt to try out better ranking schemes
(the various ranking schemes that were tried out during the development of the
project are discussed later). Better ranking schemes required storing precomputed
term weights [19] on the file system, this almost doubled the storage requirements, therefore such ranking schemes were discarded later on, and the
database schema was decomposed further into more columns. The decomposition into
more columns was done to represent the most commonly occurring sections in usual Unix man pages, for example
{\tt NAME, DESCRIPTION, LIBRARY, RETURN VALUES, EXIT STATUS, ERRORS}
etc. Such a decomposition allowed for an elaborate ranking algorithm, which could
assign different weights to each of these columns, based on their relevancy. The
final schema of the database is shown in {\bf Listing 5}
\end{description}

\subsection{apropos}
\textit{apropos} was written from scratch to use the FTS index created by
\textit{makemandb}. Since, unlike the traditional \textit{apropos}, this version
of \textit{apropos} is not limited to searching within only the {\tt NAME}
section, the resulting
number of search results is usually quite high, therefore new \textit{apropos}
employs a
sophisticated ranking algorithm to filter out the most relevant results and rank
them up. To avoid cluttering the output and make the user interface clean, the
new \textit{apropos} displays only the top 10 results by default with options
to display more results if required. During the development and testing of the
project it has been observed that, for a reasonable query, the top 10 results
are most often sufficient. \\

Another key aspect of any search application is to filter out or avoid stop-words
. Words like \textit{``the'', ``a'', ``an'', ``'this''} etc. come under the
category of stop-words, words which are \emph{very} commonly used in the
language. Stop-words usually skew the search results because of their sheer
frequency in the corpus. The usual practice in the information retrieval world
is to filter such stop-words while building the index, however, in case of this
project, it proved to be non-trivial within the given time constraints.
Therefore it was decided that, rather than eliminating stop-words from the index,
a reasonable trade off can be made by filtering out any stop-words from the
user's search query and querying the database for only the keywords which do
not come under the category of stop-words. \\

{\tt \small
\lstset{language = XML, caption={Database Schema},}
\begin{lstlisting}
The Database has three tables at present:

@@

\begin{description}
\item[2.] \hfill \\
As more and more man pages were being added to the corpus for testing purposes,
the quality of search results started to dilute. At this point of time, a
completely new approach was adopted for ranking the results. In the literature
related to information retrieval, \textit{tf-idf} [19] weights based ranking models are very common. The \textit{tf} in \textit{tf-idf} stands for \emph{Term Frequency} and \textit{idf} stands for \emph{Inverse Document Frequency}. \\

{\bf Term Frequency}: Term frequency refers to the count of the number of times
a given term
{\tt \small
t
}
appears in a given document
{\tt \small
d
} \\

@@

Term frequency is a \textit{local} factor, it is concerned only with the number
of occurrences of the search terms in one particular document at a time.
While inverse document frequency is a \textit{global} factor, in the sense that,
it indicates the discriminating power of a term. If a term appears in only a
selected set of documents, then that term separates those set of
documents from the rest. Therefore, ranking obtained by combining these two factors
brings up more relevant documents.

@@

So for a term which appears in only one document it will have
$idf = log(n)$,
while a term which appears in all the documents, it will have
$idf = log(1) = 0$

For example a term like \textit{``the''} will have a high
\textit{term frequency} in any
document, but at the same time it will have a lower \textit{inverse document frequency} (almost close to $0$), which will nullify its effect on the quality of search results.

@@

The implementation of the above scheme proved to be \emph{very} slow. It required
too many computations and all of these were required to be done for each
search result separately to compute its relevance weight. In an state of the
art search application, the index would usually store precomputed \textit{tf-idf}
weights on the file system, in which case the overhead of computing weights of
each individual search result would require very less work, leading to better
performance. An attempt was made to compute the \textit{tf-idf} weights while
indexing the man pages and store them in a separate table. This lead to high
quality search results but it also brought up a serious issue. Storing
precomputed weights on the file system, more than doubled the storage
requirements of the database index. As a concrete example, it took close
to $90 MB$ to index about $8000$ documents. Without the precomputed weights, 
the database size requirement was close to $45 MB$ for the same number of pages.
\end{description}

\begin{description}
\item[3.] \hfill \\
Since the conventional \textit{apropos} required only a few hundred kilobytes of
disk space, the disk space requirements of new \textit{apropos} seemed
hyperbolic, therefore it was decided later on to look for alternative ranking
schemes. At this point the database schema was decomposed into several columns
representing some of the most common sections found in man pages
(see {\bf Listing 5}).

At this point a fast yet sophisticated ranking algorithm was adopted.
\emph{Okapi BM25F} [15] is considered one of the most successful probabilistic
models for information retrieval. \emph{Okapi BM25F} is based on \emph{tf-idf}
scheme but it takes into account for the structure of the data. It allows for
separate weights to be assigned for different parts of a structured document to
come up with better relevance rankings. This scheme works very well for man pages
because of their highly structured content. The algorithm is described in pseudo-code below. \textit{apropos} calls this function for each of the document
obtained as part of the result set for the query and computes its relevancy
weight. The documents are ranked in decreasing order of the weights returned
from this function. \\

{\tt
\lstset{language = sh, caption={Definition of important entities used in
algorithm \ref{alg1}},}
\begin{lstlisting}
nhitcount =  Number of occurrences of
             phrase p in column c in
             current document

@@

ndocshitcount = Number of documents in
                which phrase p occurs
                in column c, at least
                once.
\end{lstlisting}
}
\begin{algorithm}
\caption{Compute Relevance Weight of a Document for a Given User Query}
\label{alg1}
\begin{algorithmic}[1]
\Require{User query {\tt q}}
\Require{Document {\tt d} whose weight needs to be computed}
\State ${\tt tf} \gets 0.0$
\State ${\tt idf} \gets 0.0$
\State ${\tt k} \gets 3.5$
\Comment 
{k is an experimentally determined parameter}
\State ${\tt doclen} \gets $ length of the current document
\State ${\tt ndoc} \gets $ Total number of documents in the corpus
\For{each phrase {\tt p} in {\tt q}}
\For {each column {\tt c} in the FTS table}
\State $w \gets $ weight for column {\tt c}
\State $idf \gets idf + $ $log(\frac{ndoc}{ndocshitcount})\times w $
\State $tf \gets tf + \frac{(nhitcount \times w)}{(nglobalhitcount \times doclen)}$
\EndFor
\EndFor
\State $score \gets $ $\frac{(tf \times idf)}{(k + tf)}$ \\
\Return $score$
\end{algorithmic}
\end{algorithm}
\end{description}

@@

\section{Related Work}
There are at least two projects which are related to this in some way.
\begin{description}
\item[man-db] \hfill \\
\textit{man-db} [11] is a complete implementation of the man page documentation
system and it is used on a number of GNU/Linux distributions. \textit{man-db}
takes an interesting approach for indexing the man page data. Unlike the
classical \textit{apropos}, it uses a Berkley DB database but still its index
is limited to the NAME section only. It adds an option `K' to \textit{man(1)} to
allow a crude full text search but it is not very efficient nor effective.
\end{description}

\begin{description}
\item[mandocdb] \hfill \\
\textit{mandocdb} [12] is more in line with the goals of this project but it
takes a novel approach. It indexes the keywords extracted from the man pages in a
key-value store using btree(3) [13]. It also comes with its own implementation
of \textit{apropos} which performs search using this key-value store. The
main key point of this implementation is that it exploits the semantic structure
but rather than indexing the complete content, it plucks out specific pieces of
information from the man pages, for example author names, function names,
header file names, etc.
from the man pages. It is more sophisticated and much more useful than classic
\textit{apropos}, but it is still essentially a keyword lookup based
implementation.
\end{description}

@@

\section{Acknowledgement}
This project has been developed as part of \emph{Google Summer of Code 2011}
[17], so thanks to \textbf{Google} for sponsoring it. Special thanks to
\textbf{Kristaps Dzonsons} who is the developer of the \textit{mdocml} [18]
project, he also helped by pointing out several issues in the parsing related
code. We would like to thank \textbf{David Young} who was involved with
this project closely and offered useful help and guidance throughout. A special
thanks goes to \textbf{Thomas Klausner} who helped in writing and reviewing
man pages for this project. Thanks to \textbf{Petra Zeidler} for administering
the GSoC program for \textit{The NetBSD Foundation}. \\

@@

>>>>

\subsection*{Abstract}
Manual pages are a key component of Unix like operating systems, they have
played a significant role in the success of Unix over the years. Man pages are
the most authentic source of reference for a system administrator or a
programmer. However, there has been a lack of good search tool to make
man pages more accessible. \\

@@

This paper discusses a new implementation of \textit{apropos} done by
Abhinav Upadhyay and mentored by Joerg Sonnenberger as part of
Google Summer of Code 2011, for The NetBSD Foundation. The goal of this project
was to replace the
conventional apropos in NetBSD with a modern version which supports full text
searches. \\

@@

This simplified design of \textit{apropos} resulted in limited utility and
usability. Only if the users know the exact keywords do they get
the appropriate results; otherwise most of
the times the searches are full of irrelevant results or possibly a dead end. 
In the modern
computing world, where hard problems like searching the World Wide Web have been
solved [3] to a sufficient degree, it makes perfect sense to leverage the
advancement in technology in order to come up with a better search tool for
man pages. \\

@@

\subsection{Lack of support for free form queries}
As noted earlier the conventional \textit{apropos} is limited to the keywords
used in the NAME section of the man pages. This means that the users do not have
a whole lot of options for specifying keywords in their queries. Besides this,
they cannot search for keywords which are not usually specified in the title of
a man page, for example a query like {\tt EINVAL} would return no results. \\

{\tt \small
\lstset{language = XML, caption={No results for free form queries}}
\begin{lstlisting}
$ apropos ``add new user''
add new user: nothing appropriate

@@

\subsection{Lack of basic language support}
Another major limitation of the classical version of \textit{apropos} is that
it is not smart enough to provide support for basic natural language processing
constructs,
like stemming or spelling corrections.
For example in the following listing it can be seen
that while \textit{apropos} returns the correct result for the query
\textit{``make directories''}, it fails when the keyword \textit{``directory''}
is used in place of \textit{``directories''}, even though the two words are based
on same root word. \\

{\tt \small
\lstset{language = XML, caption={No support for stems or words with same root},}
\begin{lstlisting}
$ apropos ``make directories''
mkdir (1) - make directories

$ apropos ``make directory''
make directory: nothing appropriate

@@

{\tt \small
\lstset{language = sh, caption={No spelling correction},}
\begin{lstlisting}
$ apropos ``copy strings''
stpcpy, stpncpy, strcpy, strncpy (3) - copy
strings

$ apropos ``coppy strings''
coppy strings: nothing appropriate
\end{lstlisting}
}

@@

\section{Solution: A new apropos}
This project proposes a very simple and straightforward solution to solve these
problems and make man pages more usable. The idea is to exploit the inherent
semantics and structure of the man pages. The \textit{mdoc(7)} [21] and
\textit{man(7)} [16] macros used for writing man pages are semantically quite
rich, those macros combined with the context of the surrounding section of the
man page in which they have been used, can act
as an indicator of the relevancy of the content. For example, the
{\tt \small
.Nm
}
macro when used inside of the
{\tt \small
NAME
}
section holds more significance than if used inside of any other section. Similarly the description of various \textit{errno} values in the
\textit{intro(2)} man page has more important information than the mention of
those \textit{errno} values in the
{\tt \small
RETURN VALUES
}
section of various man pages from section 3. \\

In essence, it should be possible
to parse and extract the structurally meaningful data
out of man pages and index them in the form of an inverted index [4]. The index
combined with a ranking algorithm which exploits the structured nature of the
data to give back more relevant results to the user, can be used to build a
high quality search interface for manual pages.
Such a search tool will solve many of the problems associated with the conventional \textit{apropos(1)} as noted
before and discussed as follows: \\

@@

\section{Implementation Details}

@@

\begin{description}
\item[Database Schema] \hfill \\
During the initial stage of the project, the structure of the database was kept
simple. The FTS table consisted of 3 columns:
{\tt
name, name\_desc, desc
}
The
{\tt
name
}
and
{\tt
name\_desc
}
columns stored the name of the man page and the one line description from the
{\tt
NAME
}
section respectively, while the
{\tt
desc
}
column stored the content from the rest of the sections. This approach worked
quite well for a small set of man pages (for example the 4000 or so man pages in
the base set of NetBSD). However, as the number of documents were increased (for example including man pages from pkgsrc), the quality of search started deteriorating. This was mainly because bulk of the parsed data was being stored
in the same column in the database and the ranking algorithm had no way of
identifying more relevant results except from identifying whether the match was found in the {\tt NAME} section or any other section. \\

To rectify this, first there was an attempt to try out better ranking schemes
(the various ranking schemes that were tried out during the development of the
project are discussed later). Better ranking schemes required storing precomputed
term weights [19] on the file system, this almost doubled the storage requirements, therefore such ranking schemes were discarded later on, and the
database schema was decomposed further into more columns. The decomposition into
more columns was done to represent the most commonly occurring sections in usual Unix man pages, for example
{\tt NAME, DESCRIPTION, LIBRARY, RETURN VALUES, EXIT STATUS, ERRORS}
etc. Such a decomposition allowed for an elaborate ranking scheme, which could
assign different weights to each of these columns, based on their relevancy. The
final schema of the database is shown in {\bf Listing 5}
\end{description}

\subsection{apropos}
\textit{apropos} was written from scratch to use the FTS index created by
\textit{makemandb}. Since, unlike the traditional \textit{apropos}, this version
of \textit{apropos} is not limited to searching within only the {\tt NAME}
section, the resulting
number of search results is usually quite high, therefore new \textit{apropos}
employs a
sophisticated ranking algorithm to filter out the most relevant results and rank
them up. To avoid cluttering the output and make the user interface clean, the
new \textit{apropos} displays only the top 10 results by default with options
to display more results if required. During the development and testing of the
project it has been observed that, for a query, most often than not the top 10
results are sufficient. \\

Another key aspect of any search application is to filter out or avoid stop-words
. Words like \textit{``the'', ``a'', ``an'', ``'this''} etc. come under the
category of stop-words, these are the words which are \emph{very} commonly used
in the
language. Stop-words usually skew the search results because of their sheer
frequency in the corpus. The usual practice in the information retrieval world
is to filter such stop-words while building the index, however, in case of this
project, it proved to be non-trivial within the given time constraints.
Therefore it was decided that, rather than eliminating stop-words from the index,
a reasonable trade off can be made by filtering out any stop-words from the
user's search query and querying the database for only the keywords which do
not come under the category of stop-words. \\

{\tt \small
\lstset{language = XML, caption={Database Schema},}
\begin{lstlisting}
The Database has three tables at present:
1. mandb
2. mandb_meta
3. mandb_links

@@

\begin{description}
\item[2.] \hfill \\
As more and more man pages were being added to the corpus for testing purposes,
the quality of search results started to dilute. At this point of time, a
completely new approach was adopted for ranking the results. In the information
retrieval literature, \textit{tf-idf} [19] weights based ranking models are very common. The \textit{tf} in \textit{tf-idf} stands for \emph{Term Frequency} and \textit{idf} stands for \emph{Inverse Document Frequency}. \\

{\bf Term Frequency}: The term frequency of a term {\tt \small t} in a document
{\tt d} refers to the count of the number of times the term {\tt \small t}
appears in the document {\tt \small d } \\

@@

Term frequency is a \textit{local} factor, it is concerned only with the number
of occurrences of the search terms in one particular document at a time.
While inverse document frequency is a \textit{global} factor, in the sense that
it indicates the discriminating power of a term. If a term appears in only a
selected set of documents, then that term separates those set of
documents from the rest. Therefore, ranking obtained by combining these two factors
brings up more relevant documents. \\

@@

So for a term which appears in only one document, it will have
$idf = log(n)$,
while a term which appears in all the documents, it will have
$idf = log(1) = 0$.
For example a term like \textit{``the''} will have a high
\textit{term frequency} in almost all the
documents, but at the same time it will have its \textit{inverse document frequency} almost close to $0$, which will nullify its effect on the quality of search results. \\

@@

The implementation of the above scheme proved to be \emph{very} slow. It required
too many computations and these were required to be done for each
search result separately to compute its relevance weight. In a state of the
art search application, the index would usually store precomputed \textit{tf-idf}
weights on the file system, in which case the overhead of computing weights of
each individual search result would require very less work, leading to better
performance. An attempt was made to compute the \textit{tf-idf} weights while
indexing the man pages and store them in a separate table. This lead to high
quality search results but it also brought up a serious issue. Storing
precomputed weights on the file system, more than doubled the storage
requirements of the database index. As a concrete example, it took close
to $90 MB$ to index about $8000$ documents. Without the precomputed weights, 
the database size requirement was close to $45 MB$ for the same number of pages.
\end{description}

\begin{description}
\item[3.] \hfill \\
Since the conventional \textit{apropos} required only a few hundred kilobytes of
disk space, the disk space requirements of new \textit{apropos} seemed
hyperbolic, therefore it was decided later on to look for alternative ranking
schemes. At this point the database schema was decomposed into several columns
representing some of the most common sections found in man pages
(see {\bf Listing 5}) and a fast yet sophisticated ranking algorithm was adopted,
to exploit this structured nature of the data. \\

\emph{Okapi BM25F} [15] is considered one of the most successful probabilistic
models for information retrieval. It is based on \emph{tf-idf}
scheme but it takes into account for the structure of the data. It allows for
separate weights to be assigned for different parts of a structured document to
come up with better relevance rankings. The exact implementation of this
algorithm did not really provide any great results and therefore it had to be
adapted and modified to suit the needs of \textit{apropos}, considering the
structure of the database schema. The actual algorithm implemented is
described in pseudo-code below. \textit{apropos} executes this function for each
of the document obtained as part of the result set for the query and computes
their relevancy weight. The documents are ranked in decreasing order of their
weights. \\

{\tt
\lstset{language = XML, caption={Definition of important entities used in
algorithm \ref{alg1}},}
\begin{lstlisting}
nhitcount =  Number of occurrences of
             phrase p in column c in
             current document

@@

ndocshitcount = Number of documents in
                which phrase p occurs
                in column c, at least
                once.
\end{lstlisting}
}
\begin{algorithm}
\caption{Compute Relevance Weight of a Document for a Given User Query}
\label{alg1}
\begin{algorithmic}[1]
\Require{User query {\tt q}}
\Require{Document {\tt d} whose weight needs to be computed}
\Require {An array {\tt weights} consisting of preassigned weights for different
columns of the FTS table}
\State ${\tt tf} \gets 0.0$
\State ${\tt idf} \gets 0.0$
\State ${\tt k} \gets 3.5$
\Comment 
{k is an experimentally determined parameter}
\State ${\tt doclen} \gets $ length of the current document
\State ${\tt ndoc} \gets $ Total number of documents in the corpus
\For{each phrase {\tt p} in {\tt q}}
\For {each column {\tt c} in the FTS table}
\State $w \gets weights[c] $
\Comment {weight for column {\tt c}}
\State $idf \gets idf + $ $log(\frac{ndoc}{ndocshitcount})\times w $
\State $tf \gets tf + \frac{(nhitcount \times w)}{(nglobalhitcount \times doclen)}$
\EndFor
\EndFor
\State $score \gets $ $\frac{(tf \times idf)}{(k + tf)}$ \\
\Return $score$
\end{algorithmic}
\end{algorithm}
\end{description}

@@

\section{Related Work}
\begin{description}
\item[man-db] \hfill \\
\textit{man-db} [11] is a complete implementation of the man page documentation
system and it is used on a number of GNU/Linux distributions. \textit{man-db}
takes an interesting approach for indexing the man page data. Unlike the
classical \textit{apropos}, it uses a Berkley DB database but still its index
is limited to the NAME section only. It adds an option `K' to \textit{man(1)} to
allow a crude full text search but it is not very efficient nor effective.
\end{description}

\begin{description}
\item[mandocdb] \hfill \\
\textit{mandocdb} [12] is part of the \textit{mdocml} project and it is more in
line with the goals of this project but it
takes a novel approach. It indexes the keywords extracted from the man pages in a
key-value store using btree(3) [13]. It also comes with its own implementation
of \textit{apropos} which performs search using this key-value store. The
key point of this implementation is that it exploits the semantic structure
but rather than indexing the complete content, it plucks out specific pieces of
information from the man pages, for example author names, function names,
header file names, etc. It is more sophisticated and much more useful than
classic
\textit{apropos}, but it is still essentially a keyword lookup based
implementation.
\end{description}

@@

\section{Acknowledgement}
This project has been developed as part of \emph{Google Summer of Code 2011}
[17], thanks to \textbf{Google} for sponsoring it. Special thanks to
\textbf{Kristaps Dzonsons} who is the developer of the \textit{mdocml} [18]
project, he also helped by pointing out several issues in the parsing related
code. Thanks to \textbf{David Young} who was involved with
this project closely and offered useful guidance and encouragement throughout. A
special thanks goes to \textbf{Thomas Klausner} who helped in writing and
reviewing the man pages for this project. Thanks to \textbf{Petra Zeidler} for
administering the GSoC program for \textit{The NetBSD Foundation}. \\

@@

\bibitem{21}
\emph{Online manual page for mdoc(7)}
\newline
{\tt
http://mdocml.bsd.lv/mdoc.7.html
}
